---
title: "broadband.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```

Russell Brandom and William Joel in an article for [The Verge](https://www.theverge.com/22418074/broadband-gap-america-map-county-microsoft-data) wrote, 

> "If broadband access was a problem before 2020, the pandemic turned it into a crisis. As everyday businesses moved online, city council meetings or court proceedings became near-inaccessible to anyone whose connection couldn’t support a Zoom call." 

But, who in America has access to broadband internet? As part of their ongoing work to improve software and service performance and security, Microsoft collected router speed data from individuals who accessed their cloud services. After aggregating and anonomyzing these data, they made these data available publicly to help researchers and policymakers understand and improve problems related to broadband access. These data give us much better insight as to the true broadband access (defined as internet download speeds of at least 25 Mbps) of Americans as, to date, most studies of broadband access have use data collated by the FCC that is based on individual Internet Service Providers' descriptions of the areas they serve. To better contextualize this, the data have also been augmented with several county-level poverty and education indicators. The variables in [broadband.csv](https://github.com/zief0002/epsy-8251/raw/master/data/broadband.csv) are:

- `state`: State postal code
- `county`: County name
- `fips`: Five-digit Federal Information Processing Standards code which uniquely identified counties and county equivalents in the United States
- `county_type`: Classification of the county as metropolitan (`metro`) or nonmetropolitan (`nonmetro`) based on the [rural-urban continuum code](https://www.ers.usda.gov/data-products/rural-urban-continuum-codes.aspx)
- `region`: Region of the country based on the [Census Bureau-designated divisions](https://en.wikipedia.org/wiki/List_of_regions_of_the_United_States)
- `fcc_availability`: Proportion of people in the county with access to fixed terrestrial broadband at speeds of 25 Mbps/3 Mbps as of the end of 2019 as measured by the FCC
- `microsoft_useage`: Proportion of people in the county that use the internet at broadband speeds estimated by Microsoft
- `pct_poverty`: Estimate of the percentage of people (of all ages) in the county living in poverty in 2019
- `fcc_diff`: The difference between the Microsoft estimate and the FCC estimate





### Preview

```{r}
# Import data
broadband = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/broadband.csv")

# View data
broadband
```


### References


Brandom, R., &amp; Joel, W. (2021, May 10). [This is a map of America's broadband problem: A county-by-county look at the broadband gap.](https://www.theverge.com/22418074/broadband-gap-america-map-county-microsoft-data) *The Verge.*

Economic Research Service, U.S. Department of Agriculture. (2021). [County-Level Data Sets.](https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/)

Microsoft. (2021). [United States Broadband Usage Percentages Dataset.](https://github.com/microsoft/USBroadbandUsagePercentages) Github repository.

