---
title: "graduation.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [graduation.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/graduation.csv) include student-level attributes for $n=2,344$ randomly sampled students who were first-year, full-time students from the 2002 cohort at a large, midwestern research university. Any students who transferred to another institution were removed from the data. The source of these data is Jones-White, Radcliffe, Lorenz, L. M., and Soria (2014). The attributes, collected for these students are:

- `student`: Student ID number in the dataset
- `degree`: Did the student obtain a degree (i.e., graduate) from the institution? (No; Yes)
- `act`: Student's ACT score (If the student reported a SAT score, a concordance table was used to transform the score to a comparable ACT score.)
- `scholarship`: Amount of scholarship offered to student (in thousands of dollars)
- `ap_courses`: Number of Advanced Placement credits at time of enrollment
- `first_gen`: Is the student a first generation college student? (No; Yes)
- `non_traditional`: Is the student a non-traditional student (older than 19 years old at the time of enrollment)? (No; Yes)



### Preview

```{r}
# Import data
grad = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/graduation.csv")

# View data
grad
```


### References

Jones-White, D. R., Radcliffe, P. M., Lorenz, L. M., &amp; Soria, K. M. (2014). Priced out?: The influence of financial aid on the educational trajectories of first-year students starting college at a large research university. *Research in Higher Education, 55*(4), 329--350. http://www.jstor.org/stable/24571776

