---
title: "hox-gpa.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [hox-gpa.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/hox-gpa.csv) were simulated by Hox et al. (2018) to represent longitudinal data for $n=200$ college students. Data were "collected" for these students over six consecutive semesters. The attributes include:

- `student`: Student ID number
- `gpa`: Student's GPA for the semester.
- `semester`: Semester the data were "collected" (i.e., measurement occasion). These values have been centered on the initial measurement occasion.
- `hours_worked`: A job status variable indicating the average number of hours the student worked each week for the semester.
- `female`: A dummy-coded indicator of the student's gender (1 = Female, 0 = Not female)
- `hs_gpa`: Student's high school GPA


### Preview

```{r}
# Import data
hox = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/hox-gpa.csv")

# View data
hox
```


### References

Hox, J. J., Moerbeek, M., &amp; van de Schoot, R. (2018). [Multilevel analysis: Techniques and applications (3rd ed.).](https://multilevel-analysis.sites.uu.nl/) Routledge.

