---
title: "minneapolis.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```

The data in [minneapolis.csv](https://github.com/zief0002/epsy-8251/raw/master/data/minneapolis.csv) were provided in Long (2012). They constitute a sample of $n=22$ students taken from a much larger dataset collected by the Minneapolis Public School District. The data were collected to comply with the No Child Left Behind Act of 2001 and began during the 2004-05 school year. The variables included in the data are:

- `student_id`: De-identified student ID number
- `reading_score`: Reading achievement score$^\dagger$. 
- `grade`: Grade-level.
- `special_ed`: Is the student recieving special education services?
- `attendance`: Proportion of attendance based on the number of school days the student attended school during the four year of the study.


$^\dagger$The reading achievement scores are based on the reading section of th Northwest Achievement Levels Test (NALT), a multiple-choice, adaptive assessment of students' academic achievement. The NALT raw scores were converted to vertically equated scaled scores using an IRT model. Higher scale scores indicate more reading achievement.


### Preview

```{r}
# Import data
mpls = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/minneapolis.csv")

# View data
mpls
```


### References

Long, J. D. (2012). *Longitudinal data analysis for the behavioral sciences using R.* Sage.


