---
title: "mn-schools.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [mnSchools.csv](https://github.com/zief0002/epsy-8251/raw/master/data/mn-schools.csv) were collected from [http://www.collegeresults.org](http://www.collegeresults.org) and contain 2011 institutional data for $n=33$ Minnesota colleges and universities. The attributes include:

- `name`: College/university name
- `grad`: Six-year graduation rate (as a percentage)
- `public`: Sector (1 = public college/university, 0 = private college/university)
- `sat`: Estimated median composite SAT score (in hundreds)
- `tuition`: Amount of tuition and required fees covering a full academic year for a typical student (in thousands of U.S. dollars)


### Preview

```{r}
# Import data
mn = readr::read_csv(file = "https://github.com/zief0002/epsy-8251/raw/master/data/mn-schools.csv")

# View data
mn
```


<!-- ### References -->


