---
title: "nba-team-data.csv and nba-player-data.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [nba-player-data.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/nba-player-data.csv) and [nba-team-data.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/nba-team-data.csv), inspired by Woltman et al. (2012), include player-level attributes for 300 NBA players, and team-level attributes for 30 different teams, respectively. 

The player-level attributes in [nba-player-data.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/nba-player-data.csv) include:

- `player:` Name of the NBA player
- `team:` Name of the NBA team for each player
- `success:` A proxy for player quality/success. This is the quantile for the player based on the player's free-throw percentage - relative to the other players in the league. Higher values indicate a more successful player (e.g., 0 = lowest 20%; 4 = highest - 20%).
- `life_satisfaction:` Score on a survey of life satisfaction. Scores range from 5 to 25, with higher scores indicating more life satisfaction.

The team-level attributes in [nba-team-data.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/nba-team-data.csv) include:

- `team:` Name of the NBA team
- `coach:` Name of the team's current coach
- `coach_experience:` This is the tercile for the coach based on years of coaching experience in the NBA (e.g., 0 = lowest third; 2 = highest third).


### Preview



**NBA team data**

```{r}
# Import data
nba_team = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/nba-team-data.csv")

# View data
nba_team
```

*NBA players data**

```{r}
# Import data
nba_player = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/nba-player-data.csv")

# View data
nba_player
```


### References

Woltman, H., Feldstain, A.,  MacKay, J. C., &amp; Rocchi, M. (2012). An introduction to hierarchical linear modeling. *Tutorials in Quantitative Methods for Psychology, 8*(1), 52--69.

