---
title: "netherlands-schools.csv and netherlands-students.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [netherlands-students.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/netherlands-students.csv) and [netherlands-schools.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/netherlands-schools.csv) include student- and school-level attributes, respectively, for $n_i=2287$ 8th-grade students from $n_j = 131$ schools in the Netherlands provided by Snijder and Bosker (2012).

The student-level attributes in [netherlands-students.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/netherlands-students.csv) include:

- `school_id`: The school ID number for each student
- `language_pre`: Language pre-test score
- `language_post`: Language post-test score
- `ses`: Measure of the socio-economic status
- `verbal_iq`: Student's score on a verbal IQ test. The variable is centered to have a mean of 0. 
- `female`: Student's sex (0 = male; 1 = female)
- `minority`: Student's minority status (0 = white; 1 = minority)

The school-level attributes in [netherlands-schools.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/netherlands-schools.csv) include:

- `school_id`: The school ID number
- `school_type`: Indicates whether the school is a public school, a Protestant private school, a Catholic private school, or a non-denominational private school
- `public`: Indicates whether the school is a public school (1) or a private school (0)
- `school_ses`: School's average socio-economic status
- `school_verbal_iq`: School's average verbal IQ score
- `school_minority`: Percentage of students at the school who are minority students



### Preview

**Student data**

```{r}
# Import student-level data
student_data = readr::read_csv(file = "~/Documents/github/epsy-8252/data/netherlands-students.csv")
# View data
student_data
```

**School data**

```{r}
# Import school-level data
school_data = readr::read_csv(file = "~/Documents/github/epsy-8252/data/netherlands-schools.csv")

#View data
school_data
```



### References

Snijders, T. A. B., &amp; Bosker, R. J. (2012). *Multilevel analysis: An introduction to basic and advanced multilevel modeling.* Sage.

