---
title: "popular-classroom.csv and popular-student.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [popular-student.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/popular-student.csv) and [popular-classroom.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/popular-classroom.csv)  includes data on 2000 different students and 100 different classrooms, respectively. The data, provided by Hox (2002), were simulated from data collected as part of a sociological study of student popularity. Student popularity, a rating on a scale of 1&ndash;10, was derived by a sociometric procedure in which all students in a class rate all the other students. Each students' popularity is the average received popularity rating.  

The attributes in [popular-student.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/popular-student.csv) include:

- `student`: Student ID (within a school)
- `class`: Classroom ID 
- `popularity`: Popularity rating of the student (0-10 scale; where 0 = very unpopular and 10 = very popular) based on having all other students in the student's class rate him/her and computing the average of those ratings.
- `teachPop`: Student's popularity as rated by the teacher. Higher values are indicative of higher popularity
- `extra`: Extraversion of the student (measured on a 10-point scale)
- `female`: Sex of the student (Male = 0; Female = 1)


The attributes in [popular-classroom.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/popular-classroom.csv) include:

- `class`: Classroom ID
- `teacherExp`: Experience level of teacher, in years



### Preview


**Student data**

```{r}
# Import data
students = readr::read_csv(file = "~/Documents/github/epsy-8252/data/popular-student.csv")

# View data
students
```


**Classroom data**

```{r}
# Import data
classrooms = readr::read_csv(file = "~/Documents/github/epsy-8252/data/popular-classroom.csv")

# View data
classrooms
```




### References

Hox, J. J. (2002). *Multilevel analysis: Techniques and applications.* Lawrence Erlbaum Associates.

