---
title: "riverview.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [riverview.csv](https://github.com/zief0002/epsy-8251/raw/master/data/riverview.csv) come from Lewis-Beck and Lewis-Beck (2016) and contain five attributes collected from a random sample of $n=32$ employees working for the city of Riverview, a hypothetical midwestern city. The attributes include:

- `education`: Years of formal education
- `income`: Annual income (in thousands of U.S. dollars)
- `seniority`: Years of seniority
- `gender`: Employee's gender
- `male`: Dummy coded gender variable (0 = Female, 1 = Male)
- `party`: Political party affiliation


### Preview

```{r}
# Import data
city = readr::read_csv(file = "https://github.com/zief0002/epsy-8251/raw/master/data/riverview.csv")

# View data
city
```


### References

Lewis-Beck, C., &amp; Lewis-Beck, M. (2016). *Applied regression: An introduction.* Sage.
