---
title: "vocabulary.csv"
output: 
  rmdformats::html_docco:
    css: 'codebooks.css'
    df_print: paged
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fontawesome)

## Global options
options(max.print = "75")

# knitr options
opts_chunk$set(
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
  )
```


The data in [vocabulary.csv](https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/vocabulary.csv), adapted from data provided by Bock (1975), come from the Laboratory School of the University of Chicago and include scaled test scores across four grades from the vocabulary section of the Cooperative Reading Test for $n=64$ students. The attributes in the dataset include:

- `id`: The student ID number
- `vocab_08`: The scaled vocabulary test score in 8th grade
- `vocab_09`: The scaled vocabulary test score in 9th grade
- `vocab_10`: The scaled vocabulary test score in 10th grade
- `vocab_11`: The scaled vocabulary test score in 11th grade
- `female`: Dummy coded sex variable (0 = Not female, 1 = Female)


### Preview

```{r}
# Import data
vocab = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/epsy-8252/master/data/vocabulary.csv")

# View data
vocab
```


### References

Bock, R. D. (1975). *Multivariate statistical methods in behavioral research.* McGraw-Hill.
